Title

### 2021-07-10 2021/Entropy/entropy.tex
Дробная часть

                      & \multicolumn{2}{l}{2D}                                                          & \multicolumn{2}{l}{3D}                                                          & \multicolumn{2}{l}{4D}                                  \\
                      & \textbf{0,002} & \textbf{0,01} & \textbf{0,002} & \textbf{0,01} & \textbf{0,002} & \textbf{0,01} \\
					  \midrule
DiRect                &   39(0)  & 29,92
 (6)                            &                                        &                                       &                &                                       \\
Базовый АГП           & 1820                                   & 841                                   & 53251,32                               & 8905,03                               & 665013,15      & 135972,78 (99)                        \\
Адаптивная схема      & 1489,01                                & 937,20                                & 69764,39                               & 12716,21                              & 583903,06      & 206869,83                             \\
АГП с деревом решений & 831,77                                 & 653,94                                & 10776,87                               & 9204,16                               & 173155,3       & 156190,43                              \\
\bottomrule
\end{tabular}
\end{specialtable}

>>>>

                      & \multicolumn{2}{l}{2D}                                                          & \multicolumn{2}{l}{3D}                                                          & \multicolumn{2}{l}{4D}                                  \\
                      & \textbf{0,002} & \textbf{0,01} & \textbf{0,002} & \textbf{0,01} & \textbf{0,002} & \textbf{0,01} \\
					  \midrule
DiRect                &   39,84(0)  & 29,92
 (6)                            &                                        &                                       &                &                                       \\
Базовый АГП           & 1820                                   & 841                                   & 53251,32                               & 8905,03                               & 665013,15      & 135972,78 (99)                        \\
Адаптивная схема      & 1489,01                                & 937,20                                & 69764,39                               & 12716,21                              & 583903,06      & 206869,83                             \\
АГП с деревом решений & 831,77                                 & 653,94                                & 10776,87                               & 9204,16                               & 173155,3       & 156190,43                              \\
\bottomrule
\end{tabular}
\end{specialtable}
